---
title: "Week 3 Assignment"
author: "Joe Barter"
date: "10/25/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

## Rubric for Week 3 Assignment

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either **GitHub Pages**, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

- The date is on the previous slide.
- A few interactive plots are on the following pages.
- The code for the European Market Indexes plot is on the last page. 
- I published to GitHub Pages.

## Slide with Simple Plot 


```{r  eval = TRUE, echo = FALSE, warning=FALSE}
library(plotly)
plot_ly(mtcars, x = ~cyl, y = ~mpg, mode = "markers",
        color = ~wt) %>%
     layout(title = 'MPG by Cyl for mtcars data')

```

## Slide with Simple BoxPlot 



```{r  eval = TRUE, echo = FALSE, warning=FALSE}
library(plotly)
plot_ly(mtcars,x= ~cyl, y = ~wt, type = "box") %>%
     layout(title = 'Wt by Cyl for mtcars data')

```


## Slide with Fancy Plot

```{r  eval = TRUE, echo = FALSE, warning=FALSE}

library (tidyr)
library ( dplyr)
library (plotly)

data("EuStockMarkets")

stocks <-  as.data.frame(EuStockMarkets) %>%
    gather(index, price) %>%
    mutate(time = rep(time(EuStockMarkets), 4))

plot_ly(stocks, x = ~time, y = ~price, color = ~index, type="scatter", mode = "lines") %>%
     layout(title = 'Stock Tracker View EuStockMarkets data')

```

## Slide with Code for Pervious Plot

The code for the previous plot is very simple.  

```{r EuStockMarkets, echo = TRUE, eval = FALSE}
library (plotly)
library (tidyr)
library ( dplyr)

data("EuStockMarkets")

stocks <-  as.data.frame(EuStockMarkets) %>%
    gather(index, price) %>%
    mutate(time = rep(time(EuStockMarkets), 4))

plot_ly(stocks, x = time, y = price, color = index)

```
